### 2019-07-10 2-Chapters/1-Chapter/chapter1.tex
A couple of changes, thanks to https://github.com/get-alex/alex#command-line

% % Main problem
% \textbf{Main problems.}
%
The root of the problems motivating this thesis are the questions of global warming and the increase of the world population.
% https://en.wikipedia.org/wiki/History_of_radio
In the last $150$ years, mankind has developed many different communication technologies, and since the late $1890$s, wireless communications between manufactured devices have been made possible, and more and more frequent in our lives.
With the advent of Internet of Things networks (IoT), billions of autonomous low-power devices are expected to be deployed worldwide, allowing a large range of different applications.
It is now a world-wide consensus that with the current trend of population increase and with the ongoing energy crisis, any newly deployed technology should be both cheap and energy efficient,
as well as adapted to serve a large number of people and devices.
%
Such IoT technologies should be able to adapt automatically to different environments and application contexts, and be as efficient as possible.
%
In addition to the usual Research and Development effort to design many different efficient radio access schemes, covering all the possible cases,
now the time has come to combine it with cheap and promising Machine Learning in order to (try to) attain the level of performance gain necessary for the IoT promises to become reality.

>>>>

% % Main problem
% \textbf{Main problems.}
%
The root of the problems motivating this thesis are the questions of global warming and the increase of the world population.
% https://en.wikipedia.org/wiki/History_of_radio
In the last $150$ years, humankind has developed different communication technologies, and since the late $1890$s, wireless communications between manufactured devices have been made possible, and more and more frequent in our lives.
With the advent of Internet of Things networks (IoT), billions of autonomous low-power devices are expected to be deployed worldwide, allowing a wide range of different applications.
It is now a world-wide consensus that with the current trend of population increase and with the ongoing energy crisis, any newly deployed technology should be both cheap and energy efficient,
as well as adapted to serve a large number of people and devices.
%
Such IoT technologies should be able to adapt automatically to different environments and application contexts, and be as efficient as possible.
%
In addition to the usual Research and Development effort to design different efficient radio access schemes, covering all the possible cases,
now the time has come to combine it with cheap and promising Machine Learning in order to (try to) attain the level of performance gain necessary for the IoT promises to become reality.

### 2019-07-10 2-Chapters/2-Chapter/chapter2.tex
A couple of changes, thanks to https://github.com/get-alex/alex#command-line

\textbf{Clinical trials} have been the first historical application of MAB models, where an arm represents a treatment, and the distribution associated with such treatment can be a Bernoulli distribution: a reward of $0$ means the drug did not heal the disease, and a reward of $1$ indicates a success. The mean of an arm, in this application, represents the mean success rate of a treatment.
Following the ``best arm identification'' model, the goal of a doctor in a clinical trial is to identify the best treatment, \ie, the arm with highest mean, in a number of trials as short as possible.
And following our model of interest, maximizing the rewards corresponds to maximizing the number of patients being successfully treated.
%
% After introducing formally the notations used in all this thesis, we review below possible applications of multi-armed bandits.

>>>>

\textbf{Clinical trials} have been the first historical application of MAB models, where an arm represents a treatment, and the distribution associated with such treatment can be a Bernoulli distribution: a reward of $0$ means the treatment did not heal the disease, and a reward of $1$ indicates a success. The mean of an arm, in this application, represents the mean success rate of a treatment.
Following the ``best arm identification'' model, the goal of a doctor in a clinical trial is to identify the best treatment, \ie, the arm with highest mean, in a number of trials as short as possible.
And following our model of interest, maximizing the rewards corresponds to maximizing the number of patients being successfully treated.
%
% After introducing formally the notations used in all this thesis, we review below possible applications of multi-armed bandits.
